\begin{longtable}{ |l|p{3cm}|l|p{5cm}|p{5cm}|l|p{6.5cm}|}
\hline
\textbf{FR\#}	&	\textbf{Requirement} & \textbf{AT\#}	&	\textbf{Description} & \textbf{Test} & \textbf{Pass/Fail} &	\textbf{Comments} \\
\hline
\endhead


DG-FR9 & Administrators will be able to see and edit all of the data in the system. & HDR-AT-1 & View all data in the health data repository & As an administrator go to the administration page for the health data repository. Check that it correctly shows data stored within the service & Pass &  \\ \hline
DG-FR9 & Administrators will be able to see and edit all of the data in the system. & HDR-AT-2 & Edit a data entry in the health data repository & Find a log entry within the health data repository. In the administration page edit an entry the save it. Check this persists. & Pass &  \\ \hline
DG-FR9 & Administrators will be able to see and edit all of the data in the system. & HDR-AT-3 & Delete a data entry in the health data repository & Find a log entry within the health data repository. In the administration page edit an entry the save it. Check this persists. & Pass &  \\ \hline
DG-FR-11 & An administrator should be able to map ingested IDs to activity types in the system & HDR-AT-4 & An administrator should be able to add a new activity type & As an administrator go to the health data repository administration page, add a new activity type. Check that it is persisted & Pass &  \\ \hline
DG-FR-11 & An administrator should be able to map ingested IDs to activity types in the system & HDR-AT-5 & An administrator should be able to map a ingest service to an activity & Edit an existing activity. Create a new mapping from an ingest service key to that activity. Check it is persisted & Pass &  \\ \hline
DG-FR-11 & An administrator should be able to map ingested IDs to activity types in the system & HDR-AT-6 & An administrator should be able to delete a mapped ingest service from an activity & Edit an existing activity with a mapping. Delete that mapping. Check this is persisted. & Pass &  \\ \hline
DG-FR-11 & An administrator should be able to map ingested IDs to activity types in the system & HDR-AT-7 & An administrator should be able to delete an activity & As an administrator remove an existing activity type. Ensure this is persisted & Pass &  \\ \hline
E-FR3-1 & The system will send out regular communications to members to update them on their own progress and that of their group. & HDR-AT-8 & The system will send regular communications to member updating on progress & Register a user account with an accessable email address, a new email the progress in the chart should be sent (one per week) & Pass &  \\ \hline
E-FR3-2 & The frequency of communications can be set by the administrator but could be from minutes to weeks for the updates. & HDR-AT-9 & The administrator should be able to change the email frequency & As an administrator go to the administration pages. Change the email frequency. Wait and ensure that a new email is sent on the update interval. & Fail &  \\ \hline
E-FR4-3 & The frequency of communications can be set by the administrator but could be from minutes to weeks for the updates. & HDR-AT-10 & The period before emailing an inactive user should be set by an administrator & As an administrator go to the administration pages. Change inactive trigger time. Wait and ensure that a new email is sent on the update interval. & Fail &  \\ \hline


\end{longtable}