\begin{longtable}{ |l|p{3cm}|l|p{5cm}|p{5cm}|l|p{6.5cm}|}
\hline
\textbf{FR\#}	&	\textbf{Requirement} & \textbf{AT\#}	&	\textbf{Description} & \textbf{Test} & \textbf{Pass/Fail} &	\textbf{Comments} \\
\hline
\endhead

HD-FR1-1 & Review data for a member - open app & HD-AT-1 & When member opens app/logs in, they are presented with their personal logged exercise statistics from the last 30 days in graph form. & User is shown their data from the last 30 days. & Pass &  \\ \hline
HD-FR1-1 & Review data for a member - view personal data & HD-AT-2 & Member can select the timeframe for viewing their personal statistics. & User can select timeframe to show data from. Data is visualised in some way. & Fail &  \\ \hline
HD-FR2-1 & Create goals, read goals, update goals - view goals & HD-AT-3 & Members can also see their personal goals from the home page. User is presented with a list of their goals (personal, group, global). Goals list includes all information about each goal: goal type, activity type, goal with metric, goal date. & 1. User has no goals. User is informed that they have no goals and are invited to create some. 2. User has goals. User is shown list of goals with: goal type (e.g. Personal), activity type (e.g. Running), goal with metric (e.g. 5km), goal date. & Pass &  \\ \hline
HD-FR2-1 & Create goals, read goals, update goals - create goal link & HD-AT-4 & Home page includes link to create new personal goal. When clicked, the user will be redirected to the 'create goal' page. & User clicks 'Create new goal' link. User is redirected to create goal page. & Pass &  \\ \hline
HD-FR2-1 & Create goals, read goals, update goals - create goal & HD-AT-5 & Goal create page includes functionality for creating a new personal goal with: activity type, goal with metric, goal date. & User selects activity type (e.g. Running) from list. User selects goal metric and inputs goal amount (e.g. 5km). User inputs goal date, can only select dates in the future. & Pass &  \\ \hline
HD-FR2-1 & Create goals, read goals, update goals - update goal link & HD-AT-6 & Goals list includes link for each personal goal for updating the goal's information. & User clicks 'Update goal' for a goal. User is redirected to goal update page. & Pass &  \\ \hline
HD-FR2-1 & Create goals, read goals, update goals - update goal & HD-AT-7 & Goal update page includes functionality for updating a current personal goal with: goal, goal date. & User inputs new goal and selects metric (e.g. 900m). User inputs new goal date, can only select dates in the future. & Pass &  \\ \hline
HD-FR2-2 & Compare goals against progress & HD-AT-8 & Whilst on the home page, the user's current progress will be represented with respect to their goals for the requested timeframe. & 1. User has no open goals. User is informed that they have no goals and is invited to create some. 2. User has open goals. Each goal with time left is represented by a progress bar, with the user's current progress on the goal represented as a percentage of it on the bar (with the progress also displayed as a percentage). End date of the goal is shown. & Pass & Note: There is no 'requested timeframe' functionality \\ \hline
E-FR1-1 & Current rankings - rankings link & HD-AT-9 & There will be a link to 'Rankings' which will redirect the user to the rankings page. . & When the user clicks on the 'Rankings' link, it will bring up the rankings page. & Pass &  \\ \hline
E-FR1-1 & Current rankings - activities per group & HD-AT-10 & There will be a table which will show the rankings for the user's group based on various activity data. If the group has activity data, the user will be able to select which activity they would like to see represented and which activity metric they would like to compare with. & 1. Group has no activity data. User is told the group has no data an is invited to add some. 2. Group has activity data. User selects activity type. Activity type and activities change. User selects which metric to compare them with, Metric changes. Displayed rank order updates.. & Pass &  \\ \hline
E-FR1-1 & Current rankings - activities per user & HD-AT-11 & There will be a table which will show the rankings for the user's activities based on their activity data. If the user has activity data, the user will be able to select which activity metric they would like to compare the activities with. & 1. User has no activity data. User is told they have no data an is invited to add some. 2. User has activity data. User selects which metric to compare them with, Metric changes. Displayed rank order updates.. & Pass &  \\ \hline
E-FR2-1 & Individual user progress & HD-AT-12 & There will be a representation of total distance covered by all of a user's activities in terms of kilometres/miles. & 1. User has no activity data. User is told they have no data and is invited to add some. 2. User has activity data. User is presented with a visualisation of their cumulative total distance covered in their combined activity data. & Pass &  \\ \hline


\end{longtable}