\begin{longtable}{ |l|p{3cm}|l|p{5cm}|p{5cm}|l|p{6.5cm}|}
\hline
\textbf{FR\#}	&	\textbf{Requirement} & \textbf{AT\#}	&	\textbf{Description} & \textbf{Test} & \textbf{Pass/Fail} &	\textbf{Comments} \\
\hline
\endhead

SL-FR1-1 & An administrator can create a ladder for a specified sport. & SL-AT-1 & When an administrator is logged in they should be able to create a new ladder & Login as an Administrator, go to the ladders and create one with a new name. Associate the ladder with an existing sport. Ensure the ladder creates correctly & Fail & An admin can create a ladder, but can not associate the ladder with a sport. \\ \hline
SL-FR2-1 & Members should be able to register to join the ladder & SL-AT-2 & A user should be able to join an existing ladder. & Login as a user, try to join a ladder. Check the current user has been added to the ladder once the user has been approved by the admin. & Pass & If the admin rejects the user, they will not be added. \\ \hline
SL-FR2-1 & Members should be able to register to join the ladder & SL-AT-3 & A user should not be able to join a ladder twice & Login as a user, try to join a ladder your already a member of. Check that this is not allowed. & Pass &  \\ \hline
SL-FR2-1 & Members should be able to register to join the ladder & SL-AT-4 & A user should not be able to join a ladder which has been deleted & On a separate machine login as an administrator. As the user start attempting to join the ladder, before submitting as the administrator delete the ladder. Check this is handled correctly. & Pass &  \\ \hline
SL-FR2-2 & Members should be able to give a small profile of themselves as a member of the ladder. & SL-AT-5 & A user should be able to save a profile & Join an existing ladder, attempt to save a new user profile. Ensure that the changes persist. & Pass &  \\ \hline
SL-FR2-3 & Profiles include a general indication of availability to play. & SL-AT-6 & Users should be able to add text which indicates their availability & As a member of an existing ladder open the profile and add a section on availability. Proceed to save the profile and check the changes persist. & Pass &  \\ \hline
SL-FR2-3 & Profiles include a general indication of availability to play. & SL-AT-7 & Users should be able to add text which indicates their availability & Login as two different users in different sessions. The first user should add text that states their availability. As the second user lookup the first user profile and view this text. & Pass &  \\ \hline
SL-FR2-4 & Profiles include a preferred location of play & SL-AT-8 & Users should be able to add text which indicates their preferred location of play & As a member of an existing ladder open the profile and add a section on location preferences. Proceed to save the profile and check the changes persist. & Pass &  \\ \hline
SL-FR2-4 & Profiles include a preferred location of play & SL-AT-9 & Users should be able to add text which indicates their preferred location of play & Login as two different users in different sessions. The first user should add text that states their location preference. As the second user lookup the first user profile and view this text. & Pass &  \\ \hline
SL-FR4-1 & Ladder members can suspend their participation & SL-AT-10 & A ladder member should be able to suspend participation in it & As a member of an existing ladder, go to your profile and click suspend. Ensure the change is persisted. & Pass &  \\ \hline
SL-FR4-2 & Ladder members can resume participation & SL-AT-11 & A ladder member should be able to resume after suspending at any point & As a member of a ladder with a suspended profile, attempt to un-suspend and check the changes persist. & Pass &  \\ \hline
SL-FR4-3 & Challenges are conceded whilst suspended & SL-AT-12 & Suspended ladder members should automatically conceded all games whilst suspended. & Login as two different users in different sessions. The first user should challenge the second. The first user should mark themselves as suspended and the second should win automatically. & Pass &  \\ \hline
SL-FR4-3 & Challenges are conceded whilst suspended & SL-AT-13 & Ladder members who unsuspend should no longer automatically conceded all games & Login as two different users in different sessions. The first user should mark and unmark themselves as suspended. The second user should challenge the first again. & Pass &  \\ \hline
SL-FR5-1 & A ladder member should be able to view the whole ladder & SL-AT-14 & As a member view the ladder we should see all other members & As a member of an existing ladder browse it, ensure all joined members are present. & Pass &  \\ \hline
SL-FR5-2 & A ladder member should be able to view the whole ladder & SL-AT-15 & As a member we should see all current positions and outstanding challenges & As a ladder member browse and ensure the ranking of all members is displayed. Issue a new challenge and check this appears with existing outstanding challenges. & Pass & When a member leaves the ladder, they take their rank with them. \\ \hline
SL-FR6-2 & Other member's profiles should show details on position, outstanding challenges and the results of the last 5 matches & SL-AT-16 & View another members current position in the ladder & In an existing league, view another member's profile and check that their current position is displayed correctly & Pass &  \\ \hline
SL-FR6-2 & Other member's profiles should show details on position, outstanding challenges and the results of the last 5 matches & SL-AT-17 & View another members current outstanding challenges in the ladder & In an existing league, view another member's profile and check that their current outstanding challenges is displayed correctly & Pass &  \\ \hline
SL-FR6-2 & Other member's profiles should show details on position, outstanding challenges and the results of the last 5 matches & SL-AT-18 & View another members last 5 matches in the ladder & In an existing league, view another member's profile and check that the last 5 matches is displayed correctly & Pass &  \\ \hline
SL-FR7-1 & A user should be able to challenge the 5 users who are ranked above them & SL-AT-19 & A user should be able to challenge 5 users above them & Go to a ladder with 7 users. As the lowest ranked user ensure you cannot challenge users below you. Attempt to challenge 5 users above you, conceding after each one. Check that you cannot challenge the user 6 ranks above & Pass &  \\ \hline
SL-FR7-1 & A user should be able to challenge the 5 users who are ranked above them & SL-AT-20 & A user should only be able to challenge those above them. & As a user who is second in a league check you can only challenge the top of the league. Switch to the user who is top, ensure nobody can be challenged. & Pass &  \\ \hline
SL-FR7-2 & Users who are suspended should not count as one of the 5 challengeable users & SL-AT-21 & A user can challenge 5 users above them regardless of suspension & Go to a ladder with 7 users, suspend one of the mid ranked users. Log in as the lowest ranked user, check that the 5 users above can be challenged as if the suspended user is not present. & Pass &  \\ \hline
SL-FR7-3 & A user can only challenge one person at a time & SL-AT-22 & Attempt to challenge multiple users at once & Once one challenge is issued a user should not be able to challenge another until they conceded or win. conceded and attempt to send another challenge which should be allowed. & Pass & The challenge label is shown but clicking on it will not challenge. \\ \hline
SL-FR7-4 & Challenges cannot be issued to users who are participating in a challenge of any kind & SL-AT-23 & Users who are already challenged cannot be challenged by someone else & Challenge another user, using a third account check that the challenged user cannot be challenged . & Pass & The challenge label is shown but clicking on it will not challenge. \\ \hline
SL-FR7-4 & Challenges cannot be issued to users who are participating in a challenge of any kind & SL-AT-24 & Users who issued a challenge cannot be challenged by someone else & Challenge another user, using a third account check that the issuing user cannot be challenged. & Pass &  \\ \hline
SL-FR8-1 & When a challenge is issued the challenger should be able to select a time and venue based on availability from the booking system & SL-AT-25 & Creating Booking & When a challenge is created, a booking should be made in the booking facilities service. & Pass &  \\ \hline
SL-FR8-1 & When a challenge is issued the challenger should be able to select a time and venue based on availability from the booking system & SL-AT-26 & Removing Booking & When a match is conceded, the original booking made should be removed. & Pass &  \\ \hline
SL-FR8-1 & When a challenge is issued the challenger should be able to select a time and venue based on availability from the booking system & SL-AT-27 & Removing Booking & When a match is reorganised, the original booking should be removed. & Pass &  \\ \hline
SL-FR8-1 & When a challenge is issued the challenger should be able to select a time and venue based on availability from the booking system & SL-AT-28 & Creating Booking & When a match is reorganised, a new booking should be made. & Pass &  \\ \hline
SL-FR8-1 & When a challenge is issued the challenger should be able to select a time and venue based on availability from the booking system & SL-AT-29 & A user issuing a challenge should be able to pick a venue and time & Challenge another user, select a venue and time to book. & Pass &  \\ \hline
SL-FR8-1 & When a challenge is issued the challenger should be able to select a time and venue based on availability from the booking system & SL-AT-30 & A user issuing a challenge should not be able to book a previously booked venue & Challenge another user, select a venue and time to book. & Pass &  \\ \hline
SL-FR8-2 & When a challenge is issued the booking system should automatically book the requested venue & SL-AT-31 & A challenge should automatically book venue & Challenge another user, select a venue and time to book. Check that the slot has correctly been booked out. & Pass &  \\ \hline
SL-FR8-3 & Communications containing the full match details should be send out to participating users & SL-AT-32 & Check an email is sent when the match is confirmed & Challenge another user and accept the match, both user emails should receive an email with the match details & Pass & On re-organising a challenge, an email is not sent with the updated date/time \\ \hline
SL-FR9-1 & Challenges users should be able to accept, concede or request a change & SL-AT-33 & Check a challenged user can perform one of the specified actions when challenged & Challenge a user choose to accept & Pass &  \\ \hline
SL-FR9-1 & Challenges users should be able to accept, concede or request a change & SL-AT-34 & Check a challenged user can perform one of the specified actions when challenged & Challenge a user choose to concede & Pass &  \\ \hline
SL-FR9-1 & Challenges users should be able to accept, concede or request a change & SL-AT-35 & Check a challenged user can perform one of the specified actions when challenged & Challenge a user, choose to re-organise the challenge on the challenged users account. & Pass &  \\ \hline
SL-FR12-1 & An administrator can remove a member of a ladder at any time & SL-AT-36 & Remove an existing member as administrator & Login as an administrator, remove a user and ensure that it is persisted. & Pass &  \\ \hline
SL-FR12-2 & An administrator can remove a member of a ladder at any time & SL-AT-37 & A removed user should concede any challenges they have associated & Be challenged by another member of the leauge, switch to an administrator. Check that removing the user correctly concedes any pending challenges against them. & Fail & If any user removes themselves from a ladder, and then rejoins, they can no longer edit the ladder. \\ \hline
SL-FR12-3 & An administrator can remove a member of a ladder at any time & SL-AT-38 & A removed user who has issued any challenges should have them withdrawn & Challenge another member of the ladder, as the administrator remove the user and check that their challenge is withdrawn against the existing user. & Fail & If any user removes themselves from a ladder, and then rejoins, they can no longer edit the ladder. \\ \hline



\end{longtable}