\subsubsection{MVC Architecture}
\par
The \textit{Booking} microservice was created to allow users to make, view, modify and remove their bookings for sport activities in their various local sports venues. Due to the fact that booking data was going to be created from either the booking microservice's interface or the \textit{Sports Ladder}, it made natural sense that the \textit{Booking} system had its own persistence layer to store data on bookings, venues, sports and facilities. 
\par
Thus \textit{FacilitiesController}, \textit{VenuesController}, \textit{SportsController} and \textit{BookingsController} were created, each performing basic CRUD operations on their respective areas: with a view for each. Later on, the concept of a 'Block' was formed to fulfil part of the requirements: for which a separate create and edit view were implemented. An API was created for each, with a simple status API to give the microservice's current online status. 
\par 
The model went through several iterations before a design was finalised. One particular issue stemmed from uncertainty about how facilities and sports would link to each-other, due to ambiguity in the client's requirements. After clarification on these requirements, the model was reworked so that a facility could only take a single sport. Thus within a venue there can be multiple facilities of the same name, but a facility-sport combination must be unique within a venue. 
\par 
As a booking takes one specific facility, it was logical to assign a venue and a sport to a facility, and for the former two to simply contain an ID and name field. This degree of normalisation resulted in more convoluted functions in the controllers/API controllers, but in return added a level of simplicity and data integrity. 
\par
Another section of the model which involved a redesign was a booking taking an end date, alongside the pre-existing start date. This was done to accommodate for the concept of a facility block, which was designed to allow an admin to: stop a facility from being booked for a period of time; stop a user from being able to make a booking in a facility during a specific time-frame. For this purpose, a booking also has a boolean specifying it is a facility booking or a facility block. Using an end date prevented an admin from having to make multiple bookings just to create a block, and allowed it to be stored as a single extended period. When creating a regular booking, a user still only provides a start date, as bookings are designed to last for exactly an hour: thus being assigned an implicit end-date. 
\subsubsection{API Endpoints}
\par 
Several API calls to \textit{Booking} are made from the microservice itself: specifically to get the sports, get the times and update the bookings. The only other microservice required to interact with the \textit{Booking} system was the \textit{Sports Ladder}. This relied on the functionality to view all of the data (sports, venues, facilities and bookings/blocks), as well as create and delete bookings. The API accommodates for this, with some slight adjustments made during the implementation of the \textit{Sports Ladder}. 
\subsubsection{User Interface Style}
\par 
Beyond access via the API endpoints, functionality was required for a user to directly make and interact with their own bookings. The requirements also made it necessary for an admin to be able to delete, modify and see all user bookings. Due to the basic nature of how this data was to be handled, there was no need for any complex visualisations. Thus all data is displayed in and removed via tables and created and updated from within simple forms. 