A number of areas of functionality were identified where it would be beneficial to package and distribute the functionality via the NuGet packaging system. The process was relatively simple, though at times it was time consuming as every release required automatic validation on the NuGet repository which could take anywhere from 5 to 90 minutes.

\subsection{biz.aberfitness.layout}
This package was created as a complementary package to the \textit{Layout Service}, enabling developers of the \textit{.NET Core} services to implement the shared layout functionality without masses of code duplication. After the package was installed only minor changes were required to enable the layout functionality, which introduced a consistent sidebar throughout most of the system. The package included all necessary logic to retrieve and display data from the \textit{Layout Service}, and also introduced a number of stylistic and behavioural changes by the inclusion of relevant JavaScript and CSS files. A third party open-source \textit{Bootstrap} theme\cite{elaadmin} was used to enhance the visual appearance of the system without the need to invest valuable development time.

\subsection{biz.aberfitness.auditlogger}
Aiming to provide many of the same benefits as the other package, namely reduction of code duplication and ease of implementation, this package provided all \textit{.NET Core} services with the ability to send audit data to the \textit{GLaDOS} service with minimal configuration required. It included all necessary classes to enable an instance of the audit logger to be made available via dependency injection wherever it was required.
