\section{Future Improvements}

  \subsection{Development Methodology}
  Many of the aforementioned issues would have been resolved by nominating a designated team leader. This person would ensure the work being completed has an accompanying issue which exists on a project board. They would also ensure that reviews are completed correctly and that different subteams are reviewing each other's code.

  \par
  Additional work meetings during the week would reduce the delay between a difficult problem being discovered and co-developers being able to help in diagnosis and resolution. It would also create another opportunity for knowledge transfer across subteams in person.

  \subsection{Localisation}
  \par
  Localisation was a system level requirement which was not completed. It was kept in mind during the start of the project, but no work was done in preparing the views for its introduction. In future projects, code reviews would be used to make sure that views are prepared for localisation before the barrier-to-entry becomes too high.

  \subsection{Access Tokens}
  There is currently no way to revoke a token using the authorization server. If a client token were leaked, a malicious party would be able use that token until expiration. Additionally, in \textit{Fitbit Ingest}, there currently is no way to revoke a token on the user's behalf. Both of these limitations were noticed after a code freeze. Additional discussion of various use-cases would have highlighted this issue earlier in development, allowing them to be rectified.

  \subsection{Automated Testing}
  \par
  Additional development time writing automated integration tests would have reduced the ongoing maintenance overhead associated with the system. All endpoints are currently tested manually as it was decided that the time spent testing did not outweigh the time writing tests in this instance. However, in the long term, the ongoing use of developer time for manual testing would have made it beneficial to write automated test suites.

\section{Fitness for Purpose}
  \subsection{Design Constraints}
  \par
  Our application stack makes use of both \textit{Java EE} and \textit{.NET Core}, as per the design constraints. These languages also provide access to many frameworks and third party libraries and packages through Nuget and Maven.

  \par
  By carefully checking the licenses of all external code and finding alternatives where required, the system is completely free of proprietary software and licensing limitations. Additionally, the use of external packages for core components, such as \textit{Identity Server} for authorization, reduces the sites future maintenance overhead.

  \par
  Finally, deployable Docker images are created for each microservice to run on the destination server. This allows the system to scale the number of instances based on an individual service's load.

  \subsection{Functional Requirements}
  \par
  Based on the client's criteria, the majority of the functional requirements were fulfilled, as seen in chapter 2. This was measured using acceptance tests, which give a rough indication of conformity to the requirements. 129 tests were performed with 12 failing, meeting 90.7\% of the requirements.
